Practical Optional Types for Clojure

### 2015-02-04 icfp15-typedclojure.tex
break out reflection calculus
more judgements
start operational semantics
start isa figure
multimethod update
change HMap app to get
add constants and other stuff
clean up syntax figure
proof
proof cases
B-Get proof
support `get` on unions in GetHMap and update

\documentclass[preprint,10pt]{sigplanconf}

@@

\usepackage{mmm}
\usepackage{mathpartir}
\usepackage{clj-grammar}
\usepackage{xcolor}
%\usepackage{url}
%\usepackage{biblatex}
\include{bibliography.bib}

@@

@@

\title{Typed Clojure}
\subtitle{An Optional Type System for Clojure, based on Typed Racket}

@@

@@

@@

\input{convert-types-figure}

>>>>

\documentclass[preprint,9pt]{sigplanconf}

@@

\usepackage{mmm}
\usepackage{mathpartir}
\usepackage{clj-grammar}
\usepackage{xcolor}
%\usepackage{url}
%\usepackage{biblatex}
\include{bibliography.bib}
\usepackage{framed}

@@

\usepackage{amsthm}

\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}

\theoremstyle{remark}
\newtheorem*{case}{Case}

\theoremstyle{remark}
\newtheorem*{subcase}{Subcase}

@@

\title{Practical Optional Types for Clojure}

@@

\begin{lstlisting}
(defn grandparent [^File f]
  (when f
    (let [f (. f (getParent))]
      (when f
        (. (new File f) (getParent))))))
\end{lstlisting}
%(some-> f (.getParent) (File.) (.getParent))

\begin{lstlisting}
(ann parent [(U nil File) -> (U nil String)])
(defn parent [^File f]
  (when f
    (.getParent f)))
\end{lstlisting}

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(defmulti tree-str (fn [e :- Expr] (:op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}

@@

\input{proof}

@@

\input{convert-types-figure}
\input{constant}

\input{isa-figure}
\input{get-method}

\input{operational-semantics}
\input{update}
